### 2014-10-03 ApTranscriptome_TR.Rmd
added some analyses for ms

@@

@@

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))
```

>>>>

Table with 'Total Transcripts' category

```{r total_table}

```

@@

Does the mean expression level for all responsive genes differ among colonies?

```{r mean_exp}
t.test(log(Ap.response.type$A22.opt), log(Ap.response.type$Ar.opt))
# expression level at optimum temp greater in Ar than A22

# non-parametric test
w4 = wilcox.test(Ap.response.type$A22.opt, 
                 Ap.response.type$Ar.opt,
                 alternative = "two.sided", paired = TRUE, conf.int = TRUE)

mean.exp <- ddply(resp.TPM.dt.sub.pred, .(colony, Transcript), summarise,
                  mean.TPM = mean(pTPM))

t.test(log(mean.exp[which(mean.exp$colony == "A22"), "mean.TPM"]), 
       log(mean.exp[which(mean.exp$colony == "Ar"), "mean.TPM"]))

# non-parametric test
w5 = wilcox.test(mean.exp[which(mean.exp$colony == "A22"), "mean.TPM"],
                 mean.exp[which(mean.exp$colony == "Ar"), "mean.TPM"],
                 alternative = "two.sided", paired = TRUE, conf.int = TRUE)

plot(log(mean.exp[which(mean.exp$colony == "A22"), "mean.TPM"]), 
     log(mean.exp[which(mean.exp$colony == "Ar"), "mean.TPM"]))
```

@@

length(which(responsive.lms.ann.type$Transcript %in% annotation.table[which(annotation.table$best.hit.to.nr != "-"), "Sequence.Name"]))

best.hit.to.nr != "-")

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, resp.TPM.dt.sub.pred, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))
```
